---
  output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.align = "center",
  dpi = 300
)
```

## Introduction

The **forensicpopdata** package provides allele frequency data for human genetic 
markers (STRs) commonly used in forensic genetics and kinship analysis. Currently 
three data sets are included:

* FBI 2015 FBI Population Data for the expanded CODIS core STR loci (`FBI2015freqs`)
* NIST 1036 Allele Frequency Data for 29 STR Loci (`NIST1036freqs`)
* UK DNA-17 Allele Frequency Data for 16 STR Loci (`UKDNA17freqs`)

In addition, it is possible to access the 
[`STRidER`](https://strider.online/frequencies) database through the 
`read_STRidER_xml` function.

## Installation

The **forensicpopdata** package is not yet available from CRAN. 
You can install the **forensicpopdata** package using the [`pak`](https://pak.r-lib.org/) package in R:

```{r}
#| eval: false
# install.packages("pak")
pak::pak("mkruijver/forensicpopdata")
```


## Usage (data sets)

The `data` function is used to load a data set.

```{r}
require(forensicpopdata)

data(NIST1036freqs)
```

The data set is a named list for each population:
```{r}
names(NIST1036freqs)
```

For each population, a list of frequencies by locus name is available:

```{r}
NIST1036freqs$AfAm$TH01
```


## Usage (STRidER)

The `read_STRidER_xml` function downloads the most recent `STRidER` database from 
`https://strider.online/`.

```{r}
freqs <- read_STRidER_xml()
```

The data set is a named list for each population:
```{r}
names(freqs)
```

For each population, a list of frequencies by locus name is available:

```{r}
freqs$`Entire Database`$TH01
```
